Article title

### 2017-07-28 paper-webserver.tex
ADD: rewrite of the bigdata solution to instead focus on pangenomes

% Drawbacks - genetics
However, these WGS-based methods only examine the underlying genetics, not the expressed phenotype; the presence of a particular gene sequence does not necessitate expression.
Correspondingly, a greater number of target sequences are identified using WGS approaches which complicates risk assessments \cite{ronholm2016navigating}, and laboratory based phenotypic tests remain inexpensive \cite{koser2012routine}.
The effectiveness of WGS-based methods also rely on the accuracy and breadth of reference datasets.

@@

% Solution via pre-computed analyses for routine tasks
Efforts such as the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive} attempt to alleviate data concerns by curating a set of known AMR genes.
In addition, agencies such as the Food and Drug Administration (FDA), which hosts GenomeTrakr \cite{allard2016practical}, the National Center for Biotechnology Information (NCBI), which hosts GenBank \cite{doi:10.1093/nar/gks1195}, and the Center for Disease Control and Prevention (CDC), which hosts PulseNet \cite{swaminathan2001pulsenet}, provide services to share genome sequences and associated metadata either openly or amongst member institutions.
Recent efforts have focused on providing modern tools for quality control of reference genomes \cite{parks2015checkm}, particularly amongst human-genome projects \cite{lee2017ngscheckmate}.
Panseq \cite{laing2010pan}, Roary \cite{page2015roary}, and chewBBACA \url{https://github.com/mickaelsilva/chewBBACA} are freely available to compute core and accessory regions and identify SNPs across a large collection of reference genomes.
Taken together, open-access initiatives and shared tooling are lessening the drawbacks of WGS-based methods, by pre-computing sufficient reference data.

% solution via modern big data approaches
For genotypic, WGS-based approaches to truly compliment laboratory-based phenotypic tests, analyses software must be faster or there must be a reasonable link between target genes and the expressed phenotype \cite{koser2012routine}.
Antimicrobial resistance testing, which is a major component of public health monitoring efforts, typically takes 18-24 hours in a reference laboratory \cite{koser2012routine} and thus WGS solutions should perform faster.
Storing results in a tiered structure, with rapid access available for retrieval and visualization while maintaining long-term data storage \cite{schatz2015biological}, would enable developers to address the current limitations \cite{de2015trends} of bioinformatics software.

>>>>

% Drawbacks - genetics
However, these WGS-based methods only examine the underlying genetics, not the expressed phenotype; the presence of a particular gene sequence does not necessitate expression.
Correspondingly, more target sequences are identified using WGS; if we take a tradition approach to making threat assessments by looking for known VFs or AMR genes, the large number of results make it difficult to guage risk \cite{ronholm2016navigating}.
The effectiveness of WGS-based methods also rely on the accuracy and breadth of reference datasets.
Agencies must also weigh the cost of developing people and knowledge in bioinformatic approaches, and laboratory based phenotypic tests remain inexpensive \cite{koser2012routine}.

@@

% Solution via software engineering
Efforts such as the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive} attempt to alleviate data concerns by curating a set of known AMR genes.
In addition, agencies such as the Food and Drug Administration (FDA), which hosts GenomeTrakr \cite{allard2016practical}, the National Center for Biotechnology Information (NCBI), which hosts GenBank \cite{doi:10.1093/nar/gks1195}, and the Center for Disease Control and Prevention (CDC), which hosts PulseNet \cite{swaminathan2001pulsenet}, provide services to share genome sequences and associated metadata either openly or amongst member institutions.
Recent efforts have focused on providing modern tools for quality control of reference genomes \cite{parks2015checkm}, particularly amongst human-genome projects \cite{lee2017ngscheckmate}.

% rewrite of bigdata approach (BIGGER bigdata)
While efforts such as CARD as important for replicating traditional results and for historical context, WGS can also be used to develop new methods using the larger datasets available.
To study entire genomes, we need methods of creating reference data encompassing all genes, both core and accessory, in a given phlogeny.
Panseq \cite{laing2010pan}, Roary \cite{page2015roary}, chewBBACA \url{https://github.com/mickaelsilva/chewBBACA}, and Graphtyper \cite{Eggertsson148403} are freely available to compute these pan-genomic regions.
These software approaches must be scalable to significantly larger datasets than those found in wet-lab approaches.
Also, for uptake by front-line clinicians and laboratories, WGS solutions should perform faster; for example, AMR genes should be determined faster than the typical 18-24 hours required in a reference laboratory \cite{koser2012routine}.
Storing results in a tiered structure, with rapid access available for retrieval and visualization while maintaining long-term data storage \cite{schatz2015biological}, would enable developers to address the current limitations \cite{de2015trends} of bioinformatics software.
